Canonical rings of $\bq$-divisors on Minimal Rational Surfaces

### 2015-08-18 surfaces-write-up/surface-write-up.tex
im: cap grobner

Next, we define an ordering on these vectors, which will be used to give a presentation for $R_D$. Although it is not
stated explicitly later, in the case that $D = \alpha_0 D_0$ is supported on a single hypersurface, the relations in
Theorem ~\ref{thm:proj-one-point} form a reduced gr\"{o}bner basis with respect to
this ordering.

>>>>

Next, we define an ordering on these vectors, which will be used to give a presentation for $R_D$. Although it is not
stated explicitly later, in the case that $D = \alpha_0 D_0$ is supported on a single hypersurface, the relations in
Theorem ~\ref{thm:proj-one-point} form a reduced Gr\"{o}bner basis with 
respect to this ordering.
